\ripple: Differentiable Waveforms for Gravitational Wave Data Analysis

### 2022-11-22 src/tex/ms.tex
add some words to fitting paragraph

\newcommand{\TE}[1]{{\color{pyGreen} #1}}
\newcommand{\te}[1]{\textbf{\color{pyGreen}(TE: #1)}}

@@

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf.pdf}
    \caption{
        Distribution of the log difference of mismatches between optimized and original model. The mean shows a 36\% decrease in mismatch. 
    }
\end{figure}

>>>>

\newcommand{\TE}[1]{{\color{pyGreen} #1}}
\newcommand{\te}[1]{\textbf{\color{pyGreen}(TE: #1)}}
\definecolor{rb4}{HTML}{27408B}
\newcommand{\kw}[1]{{\color{rb4}[KW: #1 ]}}

@@

Having an accurate waveform model is essential for many data analysis tasks in
GW, such as searching for signals and estimating source parameters given data.
While waveforms generated using numerical relativity simulations are commonly
regarded as the most accurate, they are too computationally expensive to be used
in any practical data analysis tasks. To create waveform models that can be used
in data analysis, there are a number of groups creating "approximants" of the
full numerical relativity waveforms, which are essentially simpler ansatzes that
are not as accurate but can be evaluated much faster. There are a few families
of approximants, such as the IMRPhenom family, SEOB family, and the NRSurrogate
model. \kw{cite and add a couple more sentences to introduce the waveform
families.}

Every waveform approximants have some fitting parameters that are fixed during
the process of calibrating the ansatz to NR waveforms. In the case of
IMRPhenomD, there are $\sim 220$ \kw{Kelvin check number} fitting parameters
used to capture the behavior of the amplitude and phase as a function of the
mass ratio and spins.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{../static/MM_logdiff_q148.pdf}
    \caption{ Distribution of the log difference of mismatches between optimized
        and original model. The mean shows a 36\% decrease in mismatch. }
\end{figure}
